---
output: github_document
always_allow_html: true
---

# Parallel Policy Tree

An R / Rust Package to implement a parallelized exhaustive tree search for
policy-learning. Aims to extend and speed up work done with the `policytree`
package.

# Usage

There's just one function, `exhaustive_tree()`. Use it just as you would the
`policy_tree()` function from the `policytree` package, and enjoy the parallelized speed!

Trees aren't guaranteed to be exactly the same as those produced by
`policytree` in that some leaves may be left unpruned (working on this), but
they should give the same predictions.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(exhaustivetree)
```

```{r}

n <- 400
p <- 4
d <- 3

# Classification task taken from policytree tests
X <- round(matrix(rnorm(n * p), n, p),2)
Y <- matrix(0, n, d)

tree <- exhaustive_tree(X,Y,2)

tree

```


# Installation

You must have [Rust](https://www.rust-lang.org/tools/install) installed to
compile this package.

